True versus apparent shapes of bow shocks

### 2017-12-01 papers/Paper1/sec-conclusions.tex
Finish caption for projected simulation shape figure
And improve spacing between panels

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-MHD2040-AllB7}\\[-\baselineskip]
  (b)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-HD2040}\\[-\baselineskip]
  \caption{Departure function for the shape of the contact
    discontinuity, measured from two numerical simulations of a
    \(20\,M_\odot\) main-sequence star, moving at \SI{40}{km.s^{-1}}
    through a uniform medium of density \SI{0.57}{cm^{-3}}
    \citep{Meyer:2017a}. (a)~Magnetohydrodynamic simulation with
    ambient magnetic field of strength \SI{7}{\micro G}, oriented
    parallel to the stellar velocity. (b)~Hydrodynamic simulation with
    zero magnetic field.  Blue dots show the measured shape, while the
    thick, pale-red line shows a 12th-order Chebyshev polynomial fit.
    The published shapes only extend to
    \(\theta \approx 130\)--\(150^\circ\), so we extrapolate the shapes out to
    \(\theta = 180^\circ\). Two different extrapolations are shown,
    corresponding to bows that are asymptotically closed (dashed red
    line) or open (solid red line).  For comparison, black lines show
    the departure function for wilkinoid (thick line) and cantoids
    (thin lines).}
  \label{fig:sim-depart}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_simulation}
  \caption{Projected shapes of contact discontinuity from simulations.}
  \label{fig:sim-xyp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
  \caption{Apparent projected shapes of simulations.}
  \label{fig:sim-Pi-Lambda}
\end{figure}

>>>>

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-MHD2040-AllB7}\\[-\baselineskip]
  (b)\\
  \includegraphics[width=\linewidth]
  {figs/depart-cheby-M17-HD2040}\\[-\baselineskip]
  \caption[]{Departure function for the shape of the contact
    discontinuity, measured from two numerical simulations of a
    \(20\,M_\odot\) main-sequence star, moving at \SI{40}{km.s^{-1}}
    through a uniform medium of density \SI{0.57}{cm^{-3}}
    \citep{Meyer:2017a}. (a)~Magnetohydrodynamic simulation with
    ambient magnetic field of strength \SI{7}{\micro G}, oriented
    parallel to the stellar velocity. (b)~Hydrodynamic simulation with
    zero magnetic field.  Blue dots show the measured shape, while the
    thick, pale-red line shows a 12th-order Chebyshev polynomial fit.
    The published shapes only extend to
    \(\theta \approx 130\)--\(150^\circ\), so we extrapolate the shapes out to
    \(\theta = 180^\circ\). Two different extrapolations are shown,
    corresponding to bows that are asymptotically closed (dashed red
    line) or open (solid red line).  For comparison, black lines show
    the departure function for wilkinoid (thick line) and cantoids
    (thin lines).}
  \label{fig:sim-depart}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_simulation}
  \caption[]{Projected shapes of contact discontinuity from
    simulations at different inclinations \(\abs{i}\) (varying line
    color and thickness, see key).  Top row shows magnetized
    simulation of Fig.~\ref{fig:sim-depart}a, bottom row shows
    non-magnetized simulation of Fig.~\ref{fig:sim-depart}b.  Left
    column shows asymptotically open extrapolation, right column shows
    asymptotically closed extrapolation.  All shapes are normalized to
    the projected apex distance, \(R_0'\) }
  \label{fig:sim-xyp}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/m17-planitude-alatude}
  \caption[]{Apparent projected shapes of simulations.}
  \label{fig:sim-Pi-Lambda}
\end{figure}
